The role of cognition and movement of seed-dispersing animals in shaping plant distributions

### 2024-03-07 Text/Article_ModelSeedDispersal.Rmd
Update revision

```{r figEngineering, fig.width=19.5, fig.height=19.5, include=TRUE, warning = FALSE, fig.cap="Seed-dispersing foragers can shape resource distribution | The plots show the results of 200 simulations when a seed-dispersing forager with varying level of cognition (i.e. proportion of tree locations and associated phenology known), moving choice rules or space competition intensities between trees (the two latter being simulated with an omniscient forager; left to right) was let foraging for a long time. The resulting distribution pattern was assessed by its patchiness (the tendency of trees to be aggregated into patches; larger values indicate highly aggregated trees), its alignement (the tendency of trees to form linear geometries; larger values indicate the presence of linear geometries) and spatial autocorelation in fruiting date (the tendency of trees to have fruiting dates closer/farther in time to their spatial neighbours; values close to 0 indicate negative spatial autocorrelation, values close to 1 indicate no spatial autocorrelation, values above 1 indicate positive spatial autocorrelation). The emerging movement behaviour of the forager was described in terms of routine behaviour (the tendency of the forager to target trees in a predictible way; values close to 0 indicate no predictible movement, values close to 1 indicate highly predictible movements)."}

>>>>

```{r figEngineering, fig.width=19.5, fig.height=19.5, include=TRUE, warning = FALSE, fig.cap="Seed-dispersing foragers can shape resource distribution | The plots show the results of 200 simulations when a seed-dispersing forager with varying level of cognition (i.e. proportion of tree locations and associated phenology known), moving choice rules or space competition intensities between trees (the two latter being simulated with an omniscient forager; left to right) was let foraging for a long time. The resulting distribution pattern was assessed by its patchiness (the tendency of trees to be aggregated into patches; larger values indicate highly aggregated trees), its alignement (the tendency of trees to form linear geometries; larger values indicate the presence of linear geometries) and spatial autocorelation in fruiting date (the tendency of trees to have fruiting dates closer/farther in time to their spatial neighbours; values close to -1 indicate negative spatial autocorrelation, values close to 0 indicate no spatial autocorrelation, values close to 1 indicate positive spatial autocorrelation). The emerging movement behaviour of the forager was described in terms of routine behaviour (the tendency of the forager to target trees in a predictible way; values close to 0 indicate no predictible movement, values close to 1 indicate highly predictible movements)."}
